Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-11-29 SolEnRevision_2/solar_energy_rev1.tex
Updated revisions and letter

\section{Introduction}
Recently, there has been strong research activity in solar thermal (ST) \cite{g1,g2}, solar thermophotovoltaic (STPV) \cite{g3,g4,g5,nnn1}, and thermophotovoltaic (TPV) \cite{g6,g7} \textcolor{black}{systems for converting solar and heat energy to electricity.  While hybrid PV and ST systems which convert some or all incident energy to heat for direct use (such as in a hot water heater) and in photovoltaic-thermal collectors have also seen significant advances, this review article focuses only on system which output electrical energy.  Additionally, this article focuses on high temperature STPV and ST systems due to their potentially high efficiency.}   There is strong potential for growth in these areas, especially through the use of novel nanostructured surfaces to control light absorption and emission from surfaces and to achieve high efficiency. This spectral light control can be achieved by nanostructuring of surfaces, which can strongly modify their optical properties \cite{g8,g9,RF_OptExp_2009}. Recently, significant progress has been made in the modeling and fabrication of nanostructures to control optical absorption and emission properties of surfaces. Nanostructured surfaces, for example, can be designed to be significantly more absorbing than their flat counterparts.  Similarly, surfaces can be designed to emit infrared radiation in a very narrow spectral range, providing spectrally selective surfaces~\cite{G_PS_1985, C_RPP_2014}. \textcolor{black}{ A schematic of 
an STPV device with a broad solar absorber in thermal contact with a selective emitter
is shown in Figure \ref{gfig_bbs}{\bf A}.  Figure \ref{gfig_bbs}{\bf B} and {\bf C}} show the change in emission spectra from a blackbody emitter to a selective emitter using optical nanostructures.Some typical nanostructures are depicted schematically in Fig. \ref{gfig_surfs}.

@@

\begin{figure}[ht!]
	\includegraphics[width=\textwidth]{Planar}
	\caption{\label{Fan}  Illustration of various planar structures amenable to design and modeling
by transfer matrix methods that serve as selective emitter structures.  
A 1D photonic crystal integrated into a STPV absorber/emitter structure is  
is illustrated in {\bf (a)}. Further details, including absorptivity spectra from this class of structures, can be found
in Fig. 6 and in~\cite{paper1_ref4}.  A Bragg reflector with a single absorbing defect layer,
which supports spectrally selective emission modes, is illustrated in {\bf (b)}. Further details, including emissivity spectra from this class of
structures, can be found in~\cite{BN_JApplPhys_2005}.
A structure that achieves angular and spectral selectivity by coupling evanescent photonic crystal modes
to surface phonon polariton modes in a polar layer is illustrated in {\bf (c)}.  
A structure that achieves angular and spectral selectivity by coupling incident light into Fabry-P\'{e}rot
resonances is illustrated in {\bf (d)}.  Further details, including emissivity spectra from these classes of structures, can 
be found in~\cite{LZ_JApplPhys_2006}.  Figures reproduced from 
~\cite{paper1_ref4, BN_JApplPhys_2005, LZ_JApplPhys_2006} with permission.}

@@

\subsection{Transfer Matrix Methods for planar structures}
For multi-layer planar structures, the fields can be written piece-wise as plane waves, and closed-form expressions for the wavevectors
and amplitudes of the fields in each layer can be determined from considerations of Maxwell's equations and appropriate boundary
conditions.  The boundary conditions can be expressed conveniently as matrix equations, and the amplitudes can be computed by
straightforward matrix multiplication, which forms the basis of what is called the Transfer Matrix Method~\cite{Yeh}.  The general
Transfer Matrix equations for an $L$-layer system can be written as
\begin{equation}\label{Fresnel}
  \begin{pmatrix} E_1^+  \\ E_1^-  \end{pmatrix}
  \mbox{=}
  \begin{pmatrix}
  M_{1,1} & M_{1,2} \\
  M_{2,1} & M_{2,2}  \end{pmatrix}
  \begin{pmatrix} E_L^+ \\ E_L^-  \end{pmatrix},
\end{equation}
where the elements $M_{i,j}$ depend on the material properties (the refractive index, $n$) and geometry of each layer, as well as the
frequency and polarization of incident light.  The precise form of these elements can be found in the excellent treatment by Yeh~\cite{Yeh}, and this method 
has been successfully applied for designing multi-layer absorbing structures that find wide use in TPV/STPV applications~\cite{BN_JApplPhys_2005,LZ_JApplPhys_2006,FUS_OptExp_2015}.  We interpret $E_1^+$ and $E_1^-$
as incoming and outgoing wave amplitudes on the incident side, respectively; similarly, $E_L^-$ and $E_L^+$ are incoming and outgoing wave amplitudes, respectively,
on the terminal side of the structure.  With the access to the field amplitudes and wavevectors, a number of useful quantities may be computed.
For example, the Fresnel reflection and transmission amplitudes may be computed as $r =  E_1^-/E_1^+  =  M_{2,1}/M_{1,1}$  and
$t = E_L^+/E_1^+ =  1/M_{1,1}$, respectively.  The reflection can then be calculated as $R=|r|^2$, the transmission as
$T= |t|^2 \: n_L \: {\rm cos}({\rm Re}(\theta_L)))/(n_1 \: {\rm cos}(\theta_1))$, where $n_i$  and $\theta_i$ denote the refractive index of the material of layer $i$
and the incident/refraction angle in layer $i$, respectively.  For computing the Fresnel equations, 
the field amplitude $E_L^-$ is set to zero and the amplitude $E_1^+$ is set to 1 by convention.   
The absorption can simply be computed as $A= 1-T-R$.  An additional requisite assumption is that the semi-infinite bounding 
media (layer 1 and layer L) have real refractive indices.  When this is the case, $\theta_L$ will be a real angle to satisfy conditions
required by Snell's law for absorbing media~\cite{FMS_ACSPhoton_2014,CWH_JQSRT_2005} until the transmitted wave becomes evanescent, as is the case for total internal reflection
(when ${\rm Re}(\theta_L)=90^{\circ}$).  In this case, the transmission is necessarily zero, so the interpretation of the transmission ($T$), which must be a real number between 0 and 1, is preserved in the Transfer Matrix Method for absorbing intermediate materials bounded by semi-infinite dielectric layers.   That is, the Transfer Matrix Method allows all 
intermediate layers with finite thickness to have complex refractive indices and the fields to have complex angles of reflection/transmission 
in the intermediate layers.  Thus, the Transfer Matrix Method has been successfully applied for designing multi-layer absorbing structures that find wide use in TPV/STPV applications~\cite{BN_JApplPhys_2005,LZ_JApplPhys_2006,FUS_OptExp_2015}.
The computational effort of the Transfer Matrix Method is minimal as it primarily involves the computation of the matrix elements $M_{i,j}$, which can 
be accomplished in a number of arithmetic operations that scales linearly with the number of layers in the structure.
The Transfer Matrix Equations can also be used to compute the dispersion for resonant modes in multi-layer structures.  Two
resonant modes of particular interest for multi-layer structures with one or more absorbing layers include surface plasmon polariton 
(SPP) modes~\cite{WH_PSSb_1987,Maier,Novotny,AP_NatMat_2010,FHR_SciRep_2015}, 

@@

KBG_NatMat_2013,FHR_SciRep_2015}.  SPP modes occur 
when $R \rightarrow \infty$ and   $T=0$, while the 
latter occurs
when $R \rightarrow 0$ and   $T=0$~\cite{FHR_SciRep_2015}.  SPPs involve collective electronic oscillations coupled to a propagating electromagnetic wave,
and they allow light to be guided along the 2-dimensional interface between a metal and a dielectric layer.  Because SPP wavevectors lie beyond the light-line (i.e. they have wavevector magnitudes larger than that of light propagating in the dielectric layer), excitation of SPPs can occur only under certain conditions.  A classic technique for exciting SPPs, known as the Kretschmann-Raether configuration~\cite{Raether},  involves an asymmetric dielectric/metal/dielectric structure with the refractive index of the dielectric substrate being larger than the refractive index of the dielectric superstrate.  While normally incident light cannot couple into SPPs on specular surfaces, it can couple into SPP modes at the metal/superstrate interface if it is incident from substrate side at an appropriate angle.  Using the Transfer Matrix Method to find the complex wavevector components that lead to the SPP condition ($R \rightarrow \infty$ and $T=0$) in such an asymmetric structure is equivalent to finding the angle that allows coupling of light into the SPP via Kretschmann-Raether excitation.~\cite{Raether, FHR_SciRep_2015}  Scattering at the surfaces, for example because of surface roughness or patterning with nanoparticles, can also produce large wavevector components that will allow light to couple into SPPs even at normal incidence.  Perfectly absorbing
modes can allow perfect absorption of incident light by thin absorbing layers.  Unlike SPPs, PA modes are 
non-propagating and do not necessarily lie to the right of the light line; in these cases, light can couple into perfectly absorbing modes in symmetric structures.~\cite{FHR_SciRep_2015}

@@

Given the diversity of possible planar structures, a vast parameter space exists for their design, and optimization methodologies must
be chosen judiciously.  Drevillon and Ben-Abdallah~\cite{DB_JApplPhys_2007}, as well as Nafzaoui, Drevillon, and Joulain~\cite{NDJ_JApplPhys_2012},
have developed robust optimization 
methodologies that steer multilayer structures to an optimal emissivity profile. The optimum of the emissivity
profile can be defined in a variety of ways with respect to variables including the PV cell and operating conditions.
One such approach for defining such a profile involves using the spectral efficiency of the emitter as a figure-of-merit,
where the spectral efficiency depends on the emissivity of the structure, the band-gap of the PV cell, and the target 
temperature of operation (see section {\it 4.2}).  
The emissivity can be computed from the reflectance
and transmission using the Transfer Matrix Method, enabling efficient computation of the figure-of-merit.  The design problem can then be
formulated as a maximization of the figure-of-merit in terms of the geometry and material properties of the emitter structure.
This approach has been employed to design 1D photonic crystals involving tungsten and dielectric layers with spectral efficiencies of 
about 53\% ~\cite{SKY_JPE_2015} (see Table 2).  Similarly, the Transfer 
Matrix Method can be used to design broad-band absorbers, 
and has led to the prediction of 
absorption efficiencies of 74\% in 1D photonic crystals made of tungsten 
and dielectric layers~\cite{SKY_JPE_2015} (see Table 1).

A different Transfer Matrix Method-based approach for the design of STPV components, recently introduced by us, 
leverages the observation that structures that support perfectly absorbing modes with 
certain characteristics can perform as exceptional selective emitters.  These characteristics, described in detail in
~\cite{FUS_OptExp_2015}, can be
encoded directly into a search routine that allows for the identification of structure geometries that support these modes.  The
optimization over the figure-of-merit is therefore replaced with a search for a zero in T and R, which is equivalent to finding
a zero in the transfer matrix element $M_{2,1}$ under the condition that the transmission is also zero, which can be easily satisfied.
This approach has predicted structures with spectral efficiencies of 68\% at operating temperatures of 1750 K when coupled
with common PV materials~\cite{FUS_OptExp_2015}. The TMM has also been applied by Karalis and Joannopolous to the design of planar emitter/PV cell
systems separated by subwavelength gaps that exploit near-field radiative heat transfer effects, which can exceed the far-field
limit bounded by the Planck blackbody law~\cite{KJ_SciRep_2016}.  In their approach, the dispersions of the planar emitter and PV cell are designed
such that radiative coupling between the two is only allowed at a frequency just above the PV bandgap~\cite{KJ_SciRep_2016}.

@@

\subsection{Design of patterned structures for absorption enhancement using the FDTD method}
Extensions of the previously-discussed multi-layer planar structures involve introducing geometric features in the
lateral dimension(s).  These types of structures include 2D and 3D photonic crystals, metasurfaces, metamaterials, and random-textured materials.
FDTD can be a powerful tool for designing these types of structures, and can be particularly efficient when symmetry and/or periodicity can be
exploited.  Often, these sorts of patterned materials are desired to enhance the absorption of visible light, for example, to design a perfect
absorber across the solar spectrum for solar thermophotovoltaic applications.  For such an application, the transmission, reflection, and
absorption can be computed across the spectrum as features of the surface are varied.  This procedure is illustrated in Figure~\ref{FDTD_Structures} (a) and (b), where the absorptivity of a tungsten surface patterned with pyramidal structures is computed by the FDTD method~\cite{paper1_ref4}. Similarly, Atwater and co-workers
have employed FDTD simulation to design ultra-thin patterned surfaces that behave as broad-band
``super absorbers" capable of enhancing conversion efficiency in
thin-film PV materials~\cite{AFB_NatComm_2011}.  Several of the current authors have utilized FDTD simulations to 
study and
design tungsten absorber surfaces patterned with nanocones 
with absorption efficiencies of 80\%~\cite{me1} (see Table 1),
as well as tungsten blazed grating emitter surfaces with spectral efficiencies of 59\%~\cite{me2} (see Table 2).

@@

\subsection{Summary and outlook for theoretical design methodologies}
We have described a number of powerful theoretical methodologies that can be put to use to understand, predict, and even tailor the optical
response of systems of simple or complex nanostructures.  The use of these methods, along with the ingenuity of many researchers, has
allowed the design of many novel and useful systems for radiative control.  However, as will be discussed in more detail in the remaining sections, 
overall conversion efficiencies of TPV/STPV systems often fall around 3-8\%,  well short of the theoretical limit of 85\%.  A significant challenge remains in integrating
various theoretical methodologies to model and optimize global device performance~\cite{g4,g9}.
In principle, nanostructured systems may be designed or discovered by coupling the various electrodynamics modeling approaches described above 
to global optimization methods.  Generally, an appropriate figure-of-merit to be maximized is identified, e.g. the spectral efficiency which will
be discussed in detail later, and repeated calculations of the figure-of-merit are carried out while adjusting the features of the nanostructure until 
a global optimum is found.  A plethora of multi-parameter optimization methods are available and have been used in the context of optimizing the 
optical response of nanostructures, including clustering algorithms~\cite{g4}, the Simplex method~\cite{Simplex, CH_APL_2006}, genetic algorithms~\cite{ga,DB_JApplPhys_2007}, 
particle swarms~\cite{NDJ_JApplPhys_2012, ParticleSwarm}, and Gaussian
process modeling~\cite{miller1}.  Certainly one
challenge is that an integrated TPV/STPV system must couple together various optical modalities for absorption and emission.  Usually, this requires
abandoning exact analytical approaches in favor of approximate (e.g. perturbative) analytical approaches like coupled-mode theory.  Alternatively,
researchers must rely on the use of the numerical methodologies described above, 
though this may
prove daunting from a computational point of view due to the multi-scale nature of these systems.
Global system optimization must also include considerations like thermal management along with electrodynamics, as the
requisite operating temperatures can lead to oxidation or deformation of the
constituent structures and degradation of the device performance.  
Consideration of these various system parameters creates a highly heterogeneous optimization problem
and presents significant challenges for global optimization.  
However, several authors including Celanovic and co-workers~\cite{g4}
as well as Wang and co-workers~\cite{g9} have taken on the challenge of designing systems with optimal device consideration, which have led to device efficiencies approaching 3\% and 
10\%, respectively. Considering recent interest in exploiting near-field radiative heat-transfer to enhance
TPV/STPV power and conversion efficiency~\cite{NearFieldConcentrated,SZF_NatNano_2016, KJ_SciRep_2016}, we anticipate that modeling methods that utilize
fluctuational electrodynamics~\cite{rodriguez2011,datas2013,didari2014,didari2015,edalatpour2014} will become increasingly important.
Similarly, appropriate modeling of radiative, electrical, and thermal loss mechanisms will be critical for helping to bridge
the gap between theory and experiment in the field~\cite{BDB_SciRep_2015}.

@@

Operating at such high temperatures means that there will be a large amount of thermal emission from the absorbing surface, resulting in a loss of energy.  To reduce this loss, the thermal emittance of the absorbing surface must be minimized.  Here, we will define $\epsilon_{abs}$ as the thermal emittance of an absorbing surface held at a specific temperature relative to the thermal emittance of a blackbody held at the same temperature.  This means that an absorbing surface with an $\epsilon_{abs}$ of 0.5 at 1000$^\circ$C would have half the thermal emission of a blackbody at 1000$^\circ$C.  Note that the $\epsilon_{abs}$ of a surface can change drastically with temperature if its reflectivity and absorbance change for different wavelengths of light.  This is because the spectral composition of blackbody radiation changes with temperature.  At the same time, the solar absorptance ($\alpha_{sol}$) of the surface must be maximized to ensure a high power input into the device.

@@

For emitting surfaces, a similar approach to absorbing surfaces can be taken, but with a focus on low reflectance in a narrow peak near a specific wavelength (which depends on the bandgap energy of the PV cell used), as opposed to a broad low reflectance band in the visible region.  To accurately compare emitting surfaces, their spectral efficiency is used.

The spectral efficiency is given by~\cite{me2}:
\begin{equation}\label{SpecEff}
SE = \frac{  \int_0^{\lambda_{bg}} \frac{ E_{bg} }{E_{\lambda}} \: B(\lambda, T) \: \epsilon_S (\lambda) \: d\lambda }
{\int_0^{\infty} B(\lambda,T) \: \epsilon_S (\lambda) \: d\lambda}
\end{equation}
where $E_{bg}$ is the bandgap energy of the PV cell, $E_{\lambda}$ is the energy of a photon with wavelength $\lambda$, and $\epsilon_S (\lambda)$ is the spectral emissivity of the emitting surface, approximated as the surface's absorptivity.  \textcolor{black}{This gives the relative efficiency of the emitting surface, but does not represent an overall system efficiency.  Specifically, this equation does not take into account the fill factor, open-circuit voltage, recombination losses within the PV cell, or any non-idealities in the STPV system.  The values obtained from this equation do not represent real or even potential system efficiencies, but serve as a convenient way to compare the performance of various surfaces as well as a tool for optimization.  While PV cells with external quantum efficiencies that vary by wavelength could change the optimum bandgap stated by this equation, the effect is generally small and would need to be evaluated on a case by case basis.}

>>>>

\section{Introduction}
Recently, there has been strong research activity in solar thermal (ST) \cite{g1,g2}, solar thermophotovoltaic (STPV) \cite{g3,g4,g5,nnn1}, and thermophotovoltaic (TPV) \cite{g6,g7} \textcolor{black}{systems for converting solar and heat energy to electricity.  While hybrid PV and ST systems which convert some or all incident energy to heat for direct use (such as in a hot water heater) and in photovoltaic-thermal collectors have also seen significant advances, this review article focuses only on system which output electrical energy.  Additionally, this article focuses on high temperature STPV and ST systems due to their potentially high efficiency.}   There is strong potential for growth in these areas, especially through the use of novel nanostructured surfaces to control light absorption and emission from surfaces and to achieve high efficiency. This spectral light control can be achieved by nanostructuring of surfaces, which can strongly modify their optical properties \cite{g8,g9,RF_OptExp_2009}. Recently, significant progress has been made in the modeling and fabrication of nanostructures to control optical absorption and emission properties of surfaces. Nanostructured surfaces, for example, can be designed to be significantly more absorbing than their flat counterparts.  Similarly, surfaces can be designed to emit infrared radiation in a very narrow spectral range, providing spectrally selective surfaces~\cite{G_PS_1985, C_RPP_2014}. \textcolor{black}{ A schematic of 
an STPV device with a broad solar absorber in thermal contact with a selective emitter
is shown in Figure \ref{gfig_bbs}{\bf A}.  Figure \ref{gfig_bbs}{\bf B} and {\bf C}} show the change in emission spectra from a blackbody emitter to a selective emitter using optical nanostructures.  Some typical nanostructures are depicted schematically in Fig. \ref{gfig_surfs}.

@@

\begin{figure}[ht!]
	\includegraphics[width=\textwidth]{Planar}
	\caption{\label{Fan}  Illustration of various planar structures amenable to design and modeling
by transfer matrix methods that serve as selective emitter structures.  
A 1D photonic crystal integrated into a STPV absorber/emitter structure  
is illustrated in {\bf (a)}. Further details, including absorptivity spectra from this class of structures, can be found
in Fig. 6 and in~\cite{paper1_ref4}.  A Bragg reflector with a single absorbing defect layer,
which supports spectrally selective emission modes, is illustrated in {\bf (b)}. Further details, including emissivity spectra from this class of
structures, can be found in~\cite{BN_JApplPhys_2005}.
A structure that achieves angular and spectral selectivity by coupling evanescent photonic crystal modes
to surface phonon polariton modes in a polar layer is illustrated in {\bf (c)}.  
A structure that achieves angular and spectral selectivity by coupling incident light into Fabry-P\'{e}rot
resonances is illustrated in {\bf (d)}.  Further details, including emissivity spectra from these classes of structures, can 
be found in~\cite{LZ_JApplPhys_2006}.  Figures reproduced from 
~\cite{paper1_ref4, BN_JApplPhys_2005, LZ_JApplPhys_2006} with permission.}

@@

\subsection{Transfer Matrix Methods for planar structures} For multi-layer
planar structures, the fields can be written piece-wise as plane waves,
and closed-form expressions for the wavevectors and amplitudes of the
fields in each layer can be determined from considerations of Maxwell's
equations and appropriate boundary conditions.  The boundary conditions
can be expressed conveniently as matrix equations, and the amplitudes can
be computed by straightforward matrix multiplication, which forms the
basis of what is called the Transfer Matrix Method~\cite{Yeh}.  The
general Transfer Matrix equations for an $L$-layer system can be written
as \begin{equation}\label{Fresnel}
  \begin{pmatrix} E_1^+  \\ E_1^-  \end{pmatrix} \mbox{=} \begin{pmatrix}
  M_{1,1} & M_{1,2} \\ M_{2,1} & M_{2,2}  \end{pmatrix} \begin{pmatrix}
  E_L^+ \\ E_L^-  \end{pmatrix},
\end{equation} where the elements $M_{i,j}$ depend on the material
properties (the complex refractive index, \textcolor{red}{($\tilde{n} =
n+ik$)} and geometry of each layer, as well as the frequency and
polarization of incident light.  The precise form of these elements can be
found in the excellent treatment by Yeh~\cite{Yeh}, and this method has
been successfully applied for designing multi-layer absorbing structures
that find wide use in TPV/STPV
applications~\cite{BN_JApplPhys_2005,LZ_JApplPhys_2006,FUS_OptExp_2015}.
We interpret $E_1^+$ and $E_1^-$ as incoming and outgoing wave amplitudes
on the incident side, respectively; similarly, $E_L^-$ and $E_L^+$ are
incoming and outgoing wave amplitudes, respectively, on the terminal side
of the structure.  With the access to the field amplitudes and
wavevectors, a number of useful quantities may be computed.  For example,
the Fresnel reflection and transmission amplitudes may be computed as $r =
E_1^-/E_1^+  =  M_{2,1}/M_{1,1}$  and $t = E_L^+/E_1^+ =  1/M_{1,1}$,
respectively.  The reflection can then be calculated as $R=|r|^2$, the
transmission as $T= |t|^2 \: n_L \: {\rm cos}(\theta_L))/(n_1 \: {\rm
cos}(\theta_1))$, where $n_i$  and $\theta_i$ denote the (real) refractive
index of the material of layer $i$ and the incident/refraction angle in
layer $i$, respectively.  For computing the Fresnel equations, the field
amplitude $E_L^-$ is set to zero.  The absorption can simply be computed
as $A= 1-T-R$.  An additional requisite assumption is that the
semi-infinite bounding media (layer 1 and layer L) have real refractive
indices.  When this is the case, $\theta_L$ will be a real angle to
satisfy conditions required by Snell's law for absorbing
media~\cite{FMS_ACSPhoton_2014,CWH_JQSRT_2005} until the transmitted wave
becomes evanescent, as is the case for total internal reflection (when
${\rm Re}(\theta_L)=90^{\circ}$).  In this case, the transmission is
necessarily zero, so the interpretation of the transmission ($T$), which
must be a real number between 0 and 1, is preserved in the Transfer Matrix
Method for absorbing intermediate materials bounded by semi-infinite
dielectric layers.  That is, the Transfer Matrix Method allows all
intermediate layers with finite thickness to have complex refractive
indices and the fields to have complex angles of reflection/transmission
in the intermediate layers.  Thus, the Transfer Matrix Method has been
successfully applied for designing multi-layer absorbing structures that
find wide use in TPV/STPV
applications~\cite{BN_JApplPhys_2005,LZ_JApplPhys_2006,FUS_OptExp_2015}.
The computational effort of the Transfer Matrix Method is minimal as it
primarily involves the computation of the matrix elements $M_{i,j}$, which
can be accomplished in a number of arithmetic operations that scales
linearly with the number of layers in the structure.  The Transfer Matrix
Equations can also be used to compute the dispersion for resonant modes in
multi-layer structures.  Two resonant modes of particular interest for
multi-layer structures with one or more absorbing layers include surface
plasmon polariton (SPP)
modes~\cite{WH_PSSb_1987,Maier,Novotny,AP_NatMat_2010,FHR_SciRep_2015},

@@

KBG_NatMat_2013,FHR_SciRep_2015}.  SPP modes occur when $R \rightarrow
\infty$ and   $T=0$, while the latter occurs when $R \rightarrow 0$ and
$T=0$~\cite{FHR_SciRep_2015}.  SPPs involve collective electronic
oscillations coupled to a propagating electromagnetic wave, and they allow
light to be guided along the 2-dimensional interface between a metal and a
dielectric layer.  Because SPP wavevectors lie beyond the light-line (i.e.
they have wavevector magnitudes larger than that of light propagating in
the dielectric layer), excitation of SPPs can occur only under certain
conditions.  A classic technique for exciting SPPs, known as the
Kretschmann-Raether configuration~\cite{Raether},  involves an asymmetric
dielectric/metal/dielectric structure with the refractive index of the
dielectric substrate being larger than the refractive index of the
dielectric superstrate.  While normally incident light cannot couple into
SPPs on specular surfaces, it can couple into SPP modes at the
metal/superstrate interface if it is incident from substrate side at an
appropriate angle.  Using the Transfer Matrix Method to find the complex
wavevector components that lead to the SPP condition ($R \rightarrow
\infty$ and $T=0$) in such an asymmetric structure is equivalent to
finding the angle that allows coupling of light into the SPP via
Kretschmann-Raether excitation.~\cite{Raether, FHR_SciRep_2015}
Scattering at the surfaces, for example because of surface roughness or
patterning with nanoparticles, can also produce large wavevector
components that will allow light to couple into SPPs even at normal
incidence.  Perfectly absorbing modes can allow perfect absorption of
incident light by thin absorbing layers.  Unlike SPPs, PA modes are
non-propagating and do not necessarily lie to the right of the light line;
in these cases, light can couple into perfectly absorbing modes in
symmetric structures.~\cite{FHR_SciRep_2015}

@@

Given the diversity of possible planar structures, a vast parameter space exists for their design, and optimization methodologies must
be chosen judiciously.  Drevillon and Ben-Abdallah~\cite{DB_JApplPhys_2007}, as well as Nafzaoui, Drevillon, and Joulain~\cite{NDJ_JApplPhys_2012},
have developed robust optimization 
methodologies that steer multilayer structures to an optimal emissivity profile. The optimum of the emissivity
profile can be defined in a variety of ways with respect to variables including the PV cell and operating conditions.
One such approach for defining such a profile involves using the \textcolor{red}{emitter efficiency} of the emitter as a figure-of-merit,
where the \textcolor{red}{emitter efficiency} depends on the emissivity of the structure, the band-gap of the PV cell, and the target 
temperature of operation (see section {\it 4.2}).  
The emissivity can be computed from the reflectance
and transmission using the Transfer Matrix Method, enabling efficient computation of the figure-of-merit.  The design problem can then be
formulated as a maximization of the figure-of-merit in terms of the geometry and material properties of the emitter structure.
This approach has been employed to design 1D photonic crystals involving tungsten and dielectric layers with spectral efficiencies of 
about 53\% ~\cite{SKY_JPE_2015} (see Table 2).  Similarly, the Transfer 
Matrix Method can be used to design broad-band absorbers, 
and has led to the prediction of 
absorption efficiencies of 74\% in 1D photonic crystals made of tungsten 
and dielectric layers~\cite{SKY_JPE_2015} (see Table 1).

A different Transfer Matrix Method-based approach for the design of STPV components, recently introduced by us, 
leverages the observation that structures that support perfectly absorbing modes with 
certain characteristics can perform as exceptional selective emitters.  These characteristics, described in detail in
~\cite{FUS_OptExp_2015}, can be
encoded directly into a search routine that allows for the identification of structure geometries that support these modes.  The
optimization over the figure-of-merit is therefore replaced with a search for a zero in T and R, which is equivalent to finding
a zero in the transfer matrix element $M_{2,1}$ under the condition that the transmission is also zero, which can be easily satisfied.
This approach has predicted structures with \textcolor{red}{emitter efficiencies} of 68\% at operating temperatures of 1750 K when coupled
with common PV materials~\cite{FUS_OptExp_2015}. The TMM has also been applied by Karalis and Joannopolous to the design of planar emitter/PV cell
systems separated by subwavelength gaps that exploit near-field radiative heat transfer effects, which can exceed the far-field
limit bounded by the Planck blackbody law~\cite{KJ_SciRep_2016}.  In their approach, the dispersions of the planar emitter and PV cell are designed
such that radiative coupling between the two is only allowed at a frequency just above the PV bandgap~\cite{KJ_SciRep_2016}.

@@

\subsection{Design of patterned structures for absorption enhancement using the FDTD method}
Extensions of the previously-discussed multi-layer planar structures involve introducing geometric features in the
lateral dimension(s).  These types of structures include 2D and 3D photonic crystals, metasurfaces, metamaterials, and random-textured materials.
FDTD can be a powerful tool for designing these types of structures, and can be particularly efficient when symmetry and/or periodicity can be
exploited.  Often, these sorts of patterned materials are desired to enhance the absorption of visible light, for example, to design a perfect
absorber across the solar spectrum for solar thermophotovoltaic applications.  For such an application, the transmission, reflection, and
absorption can be computed across the spectrum as features of the surface are varied.  This procedure is illustrated in Figure~\ref{FDTD_Structures} (a) and (b), where the absorptivity of a tungsten surface patterned with pyramidal structures is computed by the FDTD method~\cite{paper1_ref4}. Similarly, Atwater and co-workers
have employed FDTD simulation to design ultra-thin patterned surfaces that behave as broad-band
``super absorbers" capable of enhancing conversion efficiency in
thin-film PV materials~\cite{AFB_NatComm_2011}.  Several of the current authors have utilized FDTD simulations to 
study and
design tungsten absorber surfaces patterned with nanocones 
with absorption efficiencies of 80\%~\cite{me1} (see Table 1),
as well as tungsten blazed grating emitter surfaces with \textcolor{red}{emitter efficiencies} of 59\%~\cite{me2} (see Table 2).

@@

\subsection{Summary and outlook for theoretical design methodologies}
We have described a number of powerful theoretical methodologies that can be put to use to understand, predict, and even tailor the optical
response of systems of simple or complex nanostructures.  The use of these methods, along with the ingenuity of many researchers, has
allowed the design of many novel and useful systems for radiative control.  However, as will be discussed in more detail in the remaining sections, 
overall conversion efficiencies of TPV/STPV systems often fall around 3-8\%,  well short of the theoretical limit of 85\%.  A significant challenge remains in integrating
various theoretical methodologies to model and optimize global device performance~\cite{g4,g9}.
In principle, nanostructured systems may be designed or discovered by coupling the various electrodynamics modeling approaches described above 
to global optimization methods.  Generally, an appropriate figure-of-merit to be maximized is identified, e.g. the \textcolor{red}{emitter efficiency} which will
be discussed in detail later, and repeated calculations of the figure-of-merit are carried out while adjusting the features of the nanostructure until 
a global optimum is found.  A plethora of multi-parameter optimization methods are available and have been used in the context of optimizing the 
optical response of nanostructures, including clustering algorithms~\cite{g4}, the Simplex method~\cite{Simplex, CH_APL_2006}, genetic algorithms~\cite{ga,DB_JApplPhys_2007}, 
particle swarms~\cite{NDJ_JApplPhys_2012, ParticleSwarm}, and Gaussian
process modeling~\cite{miller1}.  Certainly one
challenge is that an integrated TPV/STPV system must couple together various optical modalities for absorption and emission.  Usually, this requires
abandoning exact analytical approaches in favor of approximate (e.g. perturbative) analytical approaches like coupled-mode theory.  Alternatively,
researchers must rely on the use of the numerical methodologies described above, 
though this may
prove daunting from a computational point of view due to the multi-scale nature of these systems.
Global system optimization must also include considerations like thermal management along with electrodynamics, as the
requisite operating temperatures can lead to oxidation or deformation of the
constituent structures and degradation of the device performance.  
Consideration of these various system parameters creates a highly heterogeneous optimization problem
and presents significant challenges for global optimization.  
However, several authors including Celanovic and co-workers~\cite{g4}
as well as Wang and co-workers~\cite{g9} have taken on the challenge of designing systems with optimal device consideration, which have led to device efficiencies approaching 3\% and 
10\%, respectively. Considering recent interest in exploiting near-field radiative heat-transfer to enhance
TPV/STPV power and conversion efficiency~\cite{NearFieldConcentrated,SZF_NatNano_2016, KJ_SciRep_2016}, we anticipate that modeling methods that utilize
fluctuational electrodynamics~\cite{rodriguez2011,datas2013,didari2014,didari2015,edalatpour2014} will become increasingly important.
Similarly, appropriate modeling of radiative, electrical, and thermal loss mechanisms will be critical for helping to bridge
the gap between theory and experiment in the field~\cite{BDB_SciRep_2015}.

@@

\textcolor{red}{Because they operate at high temperatures, absorbing surfaces will lose energy through thermal emission.}  To reduce this loss, 
the thermal emittance of the absorbing surface must be minimized.  Here, we will define $\epsilon_{abs}$ 
as the thermal emittance of an absorbing surface held at a specific temperature relative to the 
thermal emittance of a blackbody held at the same temperature.  This means that an absorbing 
surface with an $\epsilon_{abs}$ of 0.5 at 1000$^\circ$C would have half the thermal emission 
of a blackbody at 1000$^\circ$C.  Note that the $\epsilon_{abs}$ of a surface can change drastically 
with temperature if its reflectivity and absorbance change for different wavelengths of light.  
This is because the spectral composition of blackbody radiation changes with temperature.  
At the same time, the solar absorptance ($\alpha_{sol}$) of the surface must be maximized to ensure a high power input into the device.

@@

For emitting surfaces, a similar approach to absorbing surfaces can be taken, but with a focus on low reflectance in a narrow peak near a specific wavelength (which depends on the bandgap energy of the PV cell used), as opposed to a broad low reflectance band in the visible region.  To accurately compare emitting surfaces, their \textcolor{red}{emitter efficiency} is used.

The \textcolor{red}{emitter efficiency} is given by~\cite{me2}:
\begin{equation}\label{SpecEff} 
\eta_{emit} = \frac{\int_0^{\lambda_{bg}} \frac{ E_{bg} }{E_{\lambda}} \: B(\lambda, T) \:
\epsilon_S (\lambda) \: d\lambda } {\int_0^{\infty} B(\lambda,T) \:\epsilon_S (\lambda) \: d\lambda} 
\end{equation} 
where $E_{bg}$ is the
bandgap energy of the PV cell, $E_{\lambda}$ is the energy of a photon
with wavelength $\lambda$, and $\epsilon_S (\lambda)$ is the spectral
emissivity of the emitting surface, approximated as the surface's
absorptivity.   This gives the relative efficiency of the
emitting surface, but does not represent an overall system efficiency.
Specifically, this equation does not take into account the fill factor,
open-circuit voltage, recombination losses within the PV cell, or any
non-idealities in the STPV system.  The values obtained from this equation
do not represent real or even potential system efficiencies, but serve as
a convenient way to compare the performance of various surfaces as well as
a tool for optimization.  While PV cells with external quantum
efficiencies that vary by wavelength could change the optimum bandgap
stated by this equation, the effect is generally small and would need to
be evaluated on a case by case basis.  \textcolor{red}{We note that typically, the emissivity of the emitter structure
will depend upon angle, and so the angular integration cannot simply be assumed to lead to a constant factor as suggested
by Eq. (5) above; see, for example, Ref.~\cite{RF_OptExp_2009} for a definition of the emitter efficiency that depends 
explicitly upon emission angle.}
